Containers and R---the Rockerverse and beyond

### 2020-01-17 manuscript.Rmd
add stevedore

**\pkg{stevedore}** ([https://cran.r-project.org/package=stevedore](https://cran.r-project.org/package=stevedore)) 
<!-- from the CRAN description:
Work with containers over the Docker API. Rather than using system calls to interact with a docker client, using the API directly means that we can receive richer information from docker. The interface in the package is automatically generated using the 'OpenAPI' (a.k.a., 'swagger') specification, and all return values are checked in order to make them type stable.
-->
currently the most powerful Docker client in R.

>>>>

**\pkg{stevedore}** ([https://cran.r-project.org/package=stevedore](https://cran.r-project.org/package=stevedore)) is currently the most powerful Docker client in R.
It interfaces with the Docker daemon over the Docker HTTP API\footnote{} via a Unix socket on Linux or MacOS, over a named pipe on Windows, or over an HTTP/TCP connection.
The package is the only one not using system calls to the `docker` CLI for managing images and containers and easily exposes connections to remote Docker daemons, which has to be configured on the Docker level otherwise.
Using the API gives access to more information and is system independent and likely more reliable than parsing command line output.
\pkg{stevedore}'s own interface is automatically generated based on the OpenAPI specification of the Docker daemon, but still similar to the Docker CLI.
The interface is similar to R6 objects, in that a `stevedore_object` has a number of functions attached to it that can be called, and multiple specific versions of the Docker API can be supported thanks to the automatic generation\footnote{See \href{https://github.com/richfitz/stevedore/tree/master/inst/spec}{https://github.com/richfitz/stevedore/tree/master/inst/spec} and \href{https://github.com/richfitz/stevedore/blob/master/development.md}{https://github.com/richfitz/stevedore/blob/master/development.md}.}.
